---
title: "Project Proposal"
author: "ALL group member names here"
subtitle: "Due November 17 at 11:59pm"
format: pdf
---

#### Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
```

# Dataset 1 (top choice)

**Data source:**

**Brief description:**

**Research question 1:**

-   Outcome variable (include the name/description and type of variable):

**Research question 2:**

-   Outcome variable (include the name/description and type of variable):

**Load the data and provide a `glimpse()`**:

```{r data-1, warning=FALSE}

```

# Dataset 2 

**Data source:** Pew Research East Asian Religion

**Brief description:** The dataset surveys different east asian countries to see how many of them are religious and how the factors that influence them

**Research question 1:**

What variables are associated with being religious

-   Outcome variable: IsReligious, binary variable, specifies if the respondent is religious

**Research question 2:**

Do different regions have an effect on the factors that correlates with a person's bent on religion?

-   Outcome variable (include the name/description and type of variable):

**Load the data and provide a `glimpse()`**:

```{r data-1, warning=FALSE}

```



**Exploratory Plots:**

```{r plots-1}

```

# Dataset 2

**Data source:**

**Brief description:**

**Research question 1:**

-   Outcome variable (include the name/description and type of variable):

**Research question 2:**

-   Outcome variable (include the name/description and type of variable):

**Load the data and provide a `glimpse()`**:

```{r data-2, warning=FALSE}

```

**Exploratory Plots:**

```{r plots-2}

```


# 

# Team Charter

#### When will you meet as a team to work on the project components? Will these meetings be held in person or virtually?
We will do both as needed, on an ad-hoc basis.

#### What is your group policy on missing team meetings (e.g., how much advance notice should be provided)?
One day in advance. The person missing the meeting will do more work.

#### How will your team communicate (email, Slack, text messages)? What is your policy on appropriate response time (within a certain number of hours? Nights/weekends?)?
We will communicate via whatsapp, responses should be in the same day.


#### 
