---
title: "Project Proposal"
author: "Afag, Peter, Elenor, Moba the Late"
subtitle: "Due November 17 at 11:59pm"
format: pdf
---

#### Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
```

# Dataset 1 (top choice)
Police Killing Dataset
**Data source:**
https://github.com/fivethirtyeight/data/tree/master/police-killings
**Brief description:**
This dataset includes details on police killings in the United States, with variables such as location, race, gender, age, and circumstances of each incident.
**Research question 1: Is there an association between the economic conditions of a county and the racial composition of individuals involved in police-related incidents?**

- Outcome variable: race ethnicity (Nominal) – categorizes the racial/ethnic group of the deceased.
- Independent Variables:
    - _compincome_ : A measure of relative income (household income divided by county income) which indicates economic status.
    - _pov_ : Poverty level in the area, providing additional context on socio-economic conditions.


**Research question 2: Does the likelihood of an individual being armed in a police-related incident vary based on age and unemployment rate in the area?**

- Outcome variable: armed (Binary) – indicates whether the deceased was armed at the time of the incident.
- Independent Variables:
    - _age_: Age of the deceased (continuous variable).
    - _urate_: Unemployment rate in the area, which could represent socio-economic stress.
- Interaction Term: An interaction between age and urate to see if age and local unemployment influence the likelihood of individuals being armed.


**Load the data and provide a `glimpse()`**:

```{r data-1, warning=FALSE}

```

# Dataset 2 

**Data source:** Pew Research East Asian Religion

**Brief description:** The dataset surveys different east asian countries to see how many of them are religious and how the factors that influence them

**Research question 1:**

What variables are associated with being religious

-   Outcome variable: IsReligious, binary variable, specifies if the respondent is religious

**Research question 2:**

Do different regions have an effect on the factors that correlates with a person's bent on religion?

-   Outcome variable (include the name/description and type of variable):

**Load the data and provide a `glimpse()`**:

```{r data-1, warning=FALSE}

```



**Exploratory Plots:**

```{r plots-1}

```

# 

# Team Charter

#### When will you meet as a team to work on the project components? Will these meetings be held in person or virtually?
We will do both as needed, on an ad-hoc basis.

#### What is your group policy on missing team meetings (e.g., how much advance notice should be provided)?
One day in advance. The person missing the meeting will do more work.

#### How will your team communicate (email, Slack, text messages)? What is your policy on appropriate response time (within a certain number of hours? Nights/weekends?)?
We will communicate via whatsapp, responses should be in the same day.


#### 
